Modeling vertical-axis cross-flow turbine wakes

### 2015-08-12 paper.tex
Remove incorrect statement
Add verification figure and 3-D mesh count; closes #23 and closes #6

The $k$--$\omega$ SST and Spalart--Allmaras RANS model cases were verified for
convergence of the turbine mean power coefficient with respect to grid spacing
and timestep. The grid topology was fixed, but the number of cells per unit
length were scaled proportionally, maintaining the same background mesh cell
aspect ratio. Results for this parameter sweep are shown in 
Figure~\ref{fig:spatial-grid-dep}, from which the final number of streamwise
grid points $N_x = 70$ was chosen. This corresponds to a total cell count of approximately $5 \times 10^4$ for the 2-D cases and 
\todo[inline]{Get total cell count for 3-D case.}

\begin{figure}[ht]
\caption{Spatial grid dependence for the SST (a) and Spalart--Allmaras (b) 
turbulence models for fixed timesteps.}
\label{fig:spatial-grid-dep}
\end{figure}

Timestep dependence was studied using the $N_x=70$ grid, the results from which
are shown in Figure~\ref{fig:timestep-dep}. It was seen that the
Spalart--Allmaras model converged well with decreasing timestep, leading to a
final timestep of 0.001 s. The results from the SST model show a local minimum,
at $\Delta t = 0.002$ s, which was the final timestep chosen to run the
simulations.

\begin{figure}[ht]
\caption{Spatial grid dependence for the SST (a) and Spalart--Allmaras (b) 
turbulence models for a grid with $N_x=70$.}
\label{fig:timestep-dep}
\end{figure}

@@

We see that the side of the turbine with the upwind facing blade ($+y$), despite
having regions of high turbulence intensity, is actually more dominated by
unsteadiness in the Reynolds-averaged velocity, rather than the model's
turbulence kinetic energy.

>>>>

The $k$--$\omega$ SST and Spalart--Allmaras RANS model cases were verified for
convergence of the turbine mean power coefficient with respect to grid spacing
and timestep. The grid topology was fixed, but the number of cells per unit
length were scaled proportionally, maintaining the same background mesh cell
aspect ratio. Results for this parameter sweep are shown in
Figure~\ref{fig:spatial-grid-dep}, from which the final number of streamwise
grid points $N_x = 70$ was chosen. This corresponds to a total cell count of
approximately $5 \times 10^4$ for the 2-D cases and 16 million for the 3-D case.

\begin{figure}[ht]
    \centering

    \includegraphics[width=0.9\textwidth]{figures/verification}

    \caption{Time step (left) and grid size (right) dependence for the 2-D case
        with both the SST and SA turbulence models. Time step dependence was carried
        out with $N_x=70$ and grid size dependence with the time steps annotated for
        each turbulence model.}

    \label{fig:spatial-grid-dep}
\end{figure}

Time step dependence was studied using the $N_x=70$ grid, the results from which
are shown in Figure~\ref{fig:timestep-dep}. It was seen that the
Spalart--Allmaras model converged well with decreasing time step, leading to a
final time step of 0.001 s. The results from the SST model show a local minimum,
at $\Delta t = 0.002$ s, which was the final time step chosen to run the
simulations.

\todo[inline]{Find some examples in the literature where time steps are much
    larger.}

@@
